---
title: "Project 3"
author: "Boareto"
output:
  slidy_presentation: default
  ioslides_presentation: default
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Challenge
1. Write a shiny application with associated supporting documentation. The documentation should be thought of as whatever a user will need to get started using your application.
2. Deploy the application on Rstudio's shiny server
3. Share the application link by pasting it into the provided text box
4. Share your server.R and ui.R code on github

## Tha is about

The Galton Heights dataset has used to predict a child's height based on the gender and parent's average height.

## Plot
In the scatterplot below are represented the data and the predict fit line
```{r plot}
library(HistData)
library(ggplot2)
data(GaltonFamilies)
gf <- GaltonFamilies
gf$midparentheight=(gf$father+gf$mother)/2
gsplt2 <- ggplot(data = gf, aes(x = childHeight, y = midparentheight)) +
  geom_point(aes(colour = gender)) +
  geom_smooth(size = .5)
gsplt2
```

## THANKS
more details: https://github.com/pedroboareto/Product.git